---
title: "An Introduction to the Binomial Distribution"
author: "Andre N. Sha"
date: "r Sys.Date()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{An Introduction to the Binomial Distribution}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(binomial)
library(ggplot2)
```

## Binomial

The package `"binomial"` allows the user to experiment with various basic binomial calculations and create binomial distribution plots.

## Different Functions in "binomial"

There are many different functions in the `"binomial"` package. They include bin_choose, bin_probability, bin_distribution, bin_cumulative, and bin_variable.

bin_choose and bin_probability use 'n' trials and 'k' successes as their parameters, and their output calculates the binomial coefficient of a given binomial distribution, and the probability of success in their trials respectively. bin_probability also requires you to input the probability of the event.  

bin_distribution calculates a binomial distribution table, returning a data frame and plotting it.

bin_cumulative calculates the cumulative probability.

bin_variable is a function that returns a list of named elements 'trials' and 'prob'
trials and probability.


## Step 1. Creating a "bin_var"

The first step is to create a `"bin_var"` object with the function `bin_variable()` which takes in two different arguments: `trials` and `prob`:

```{r}
bin_var <- bin_variable(trials = 40, prob = 0.5)
print(bin_var)
```

In this example, `bin_var` thus follows the distribution Bin(40,.5).

## Step 2. Summary statistics

Now that we have `bin_var` object, we can find the full summary statistics of `bin_var`.

```{r}
summary(bin_var)
```


## Step 3. Individual Computations

With this package, we can find the mean, variance, mode, skewness, and kurtosis of a given binomial distribution. The package also contains different functions that can can be used to compute each summary statistic individually. 

```{r}
bin_mean(trials = 40, prob = 0.5)
bin_variance(trials = 40, prob = 0.5)
bin_mode(trials = 40, prob = 0.5)
bin_skewness(trials = 40, prob = 0.5)
bin_kurtosis(trials = 40, prob = 0.5)
```


## Step 4. Building Tables and Making Plots

As stated before, `bin_distribution()` creates tables of the given binomial probability distribution.

```{r, fig.show='hold'}
bin_dis <- bin_distribution(trials = 40, prob = 0.5)
bin_dis
```

To visualize this, you can just use use the `plot()` function.

```{r}
plot(bin_dis)
```

You can also use `bin_cumulative()` to create a table of the cumulative binomial probability distribution.

```{r, fig.show='hold'}
bin_cum <- bin_cumulative(trials = 40, prob = 0.5)
bin_cum
```

Just like the bin_distribution() function, you can visualize the probability distribution using the `plot()` function.

```{r}
plot(bin_cum)
